\documentclass[a4 paper, 12pt]{article} % Font size (can be 10pt, 11pt or 12pt) and paper size (remove a4paper for US letter paper)
\usepackage{txfonts} %设置字体为times new Roman
\usepackage{setspace} %可以为某一段落设置行间距
\usepackage[protrusion=true,expansion=true]{microtype} % Better typography
\usepackage{graphicx} % Required for including pictures
\usepackage{wrapfig} % Allows in-line images
\usepackage{geometry} %自由设置上下左右的页边距
\geometry{left=3.18cm,right=3.18cm,top=2.54cm,bottom=2.54cm}
\usepackage[T1]{fontenc} % Required for accented characters
\linespread{2} % Change line spacing here, Palatino benefits from a slight increase by default 设置行间距
\usepackage{booktabs}
\usepackage{float}%插图片到你代码相应的位置
\usepackage{multirow, makecell}
\usepackage{indentfirst} %段首空两个字符
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{mathrsfs}
\usepackage{threeparttable}
\usepackage{dcolumn}
\usepackage{multirow} %做复杂表格
\usepackage{abstract} % Allows abstract customization
\renewcommand{\abstractnamefont}{\normalfont\bfseries} % Set the "Abstract" text to bold
\renewcommand{\abstracttextfont}{\normalfont\small} % Set the abstract itself to small italic text
\usepackage{caption}  %给表格和图编号。上下标题
\captionsetup{justification=centering}
\usepackage{subfigure}%并排放图
\usepackage{listings}
\usepackage{xcolor}
\lstset{numbers=left, %设置行号位置
        numberstyle=\tiny, %设置行号大小
        keywordstyle=\color{blue}, %设置关键字颜色
        commentstyle=\color[cmyk]{1,0,1,0}, %设置注释颜色
        frame=single, %设置边框格式
        escapeinside=``, %逃逸字符(1左面的键)，用于显示中文
        %breaklines, %自动折行
        extendedchars=false, %解决代码跨页时，章节标题，页眉等汉字不显示的问题
        xleftmargin=2em,xrightmargin=2em, aboveskip=1em, %设置边距
        tabsize=4, %设置tab空格数
        showspaces=false %不显示空格
       }
%----------------------------------------------------------------------------------------
%        
%----------------------------------------------------------------------------------------
\makeatletter
\renewcommand\@biblabel[1]{\textbf{#1.}} % Change the square brackets for each bibliography item from '[1]' to '1.'
\renewcommand{\@listI}{\itemsep=0pt} % Reduce the space between items in the itemize and enumerate environments and the bibliography 使item间的间距减小

\renewcommand{\maketitle}{ % Customize the title - do not edit title and author name here, see the TITLE block below
%----------------------------------------------------------------------------------------
%       设置标题格式
%----------------------------------------------------------------------------------------
\begin{center} % 标题放置中间 align 右
{\huge\@title} % Increase the font size of the title设置标题的格式
\vspace{30pt} % Some vertical space between the title and author name标题与作者之间的间距
{\large\@author} % Author name
%\\\@date % Date
\vspace{8pt} % Some vertical space between the author block and abstract作者与abstract之间的距离
\end{center}
}
%----------------------------------------------------------------------------------------
%	结束paper的整体设置，开始TITLE
%----------------------------------------------------------------------------------------

\title{\textbf{Simulate Random Numbers Using Halton Sequence}} % Subtitle
\author{\textsc{} % Author
\\{ Group 7   \   Project No.1}} % Institution
%----------------------------------------------------------------------------------------

\begin{document}
\maketitle % Print the title section
\section{Introduction about Halton sequence}
\par In statistics, Halton sequences are sequences used to generate points in space for numerical methods such as Monte Carlo simulations. Although these sequences are deterministic, they are of low discrepancy, that is, appear to be random for many purposes. They were first introduced in 1960 and are an example of a quasi-random number sequence. They generalise the one-dimensional van der Corput sequences, consult that article for a precise definition.
\section{Example About Halton sequence}
\par Example of Halton sequence used to generate points in $(0,1)\times (0,1)$ in $R^{2}$.The Halton sequence is constructed according to a deterministic method that uses coprime numbers as its bases. As a simple example, let's take one dimension of the Halton sequence to be based on 2 and the other on 3. To generate the sequence for 2, we start by dividing the interval (0,1) in half, then in fourths, eighths, etc., which generates
$$\frac{1}{2},\frac{1}{4},\frac{3}{4},\frac{1}{8},\frac{5}{8},\frac{3}{8},\frac{7}{8},\frac{1}{16},\frac{9}{16},\cdot\cdot\cdot$$
and to generate the sequence for 3, we divide the interval $(0,1)$ in thirds, then ninths,twenty-sevenths, etc., which generates
$$\frac{1}{3},\frac{2}{3},\frac{1}{9},\frac{4}{9},\frac{7}{9},\frac{2}{9},\frac{1}{27},\cdot\cdot\cdot$$
When we pair them up, we get a sequence of points in a unit square:
$$(\frac{1}{2},\frac{1}{3}),(\frac{1}{4},\frac{2}{3}),(\frac{3}{4},\frac{1}{9}),(\frac{1}{8},\frac{4}{9}),
(\frac{5}{8},\frac{7}{9}),(\frac{3}{8},\frac{2}{9}),(\frac{7}{8},\frac{1}{27}),\cdot\cdot\cdot$$
\par Even though standard Halton sequences perform very well in low dimensions, correlation problems have been noted between sequences generated from higher primes. For example, if we started with the primes 17 and 19, the first 16 pairs of points $(\frac{1}{17},\frac{1}{19}),(\frac{2}{17},\frac{2}{19}),(\frac{3}{17},\frac{3}{19})\cdot\cdot\cdot
(\frac{16}{17},\frac{16}{19})$,have perfect linear correlation. To avoid this, it is common to drop the first 20 entries, or some other predetermined number depending on the primes chosen. In order to deal with this problem, various other methods have been proposed; one of the most prominent solutions is the scrambled Halton sequence, which uses permutations of the coefficients used in the construction of the standard sequence. Another solution is using leaped Halton, just skipping points.If you use e.g. only each 409th point (also other prime numbers not used in the Halton core sequence are possible), then you can achieve significant improvements.
\section{Implementation in codes in R and MATLAB}
\par Our group simulate n random numbers with base b between 0 and 1 using Halton sequence , the R code are as follows:
\begin{spacing}{1}
\begin{frame}

\begin{lstlisting}[language= R]
HaltonSingle<-function(n,b){
            n0<-n
            hn<-0
            f<-1/b
            while (n0>0) {
                        n1<-floor(n0/b)
                        r<-n0-n1*b
                        hn<-hn+f*r
                        f<-f/b
                        n0<-n1
            }
            hn
            }
HaltonSingle(5,2)
haltontotal<-function(n,b){
            hs<-rep(0,n)
            for(i in 1:n){
                        hs[i]<-HaltonSingle(i,b)

            }
            hs
}
haltontotal(5,2)
\end{lstlisting}

\end{frame}
\end{spacing}
\par \
\par The MATLAB code are as follows:
\begin{spacing}{1}
\begin{frame}

\begin{lstlisting}[language=R]
function hs = haltontotal(n,b)
hs =zeros(n,1);
for i=1:n
hs(i)=HaltonSingle(i,b)
end

function hn = haltonSingle(n,b)
n0=n;
hn=0;
f=1/b;
while(n0>0)
n1=floor(n0/b);
r=n0-n1*b;
hn=hn+f*r;
f=f/b;
n0=n1;
end
\end{lstlisting}

\end{frame}
\end{spacing}


\section{Conclusion}
\par From R ,  We can get the output results
\begin{spacing]{1}
\begin{frame}

\begin{lstlisting}[language=R]
> HaltonSingle(5,2)
[1] 0.625
> haltontotal(5,2)
[1] 0.500 0.250 0.750 0.125 0.625
\end{lstlisting}

\end{frame}
\end{spacing}
\par Also, In MATLAB, we can get the same results. Then we finish our simulation.
\end{document}
